Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-04-17 draft/paper1.tex
Intro: goals

    In this paper, we take advantage of new high-resolution (median 
    FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
    limit $> 28.5$\sb) imaging from the Hyper-Suprime Cam (HSC) Subaru Strategic 
    Program \citep[SSP,][]{HSCDR1} to characterize the outer parts of massive galaxies 
    as a function of their properties. 
    The deep imaging depth and excellent seeing conditions of HSC images make them 
    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
    large radii. 
    \update{
    With the help of reliable spectroscopic and photometric redshift 
    (e.g. the ones for \redm{} clusters, \citealt{Rykoff2014}; \citealt{Rozo2015b}),
    we select a large sample (${\sim} 7000$) of massive central galaxies at 
    $0.3 < z < 0.5$ using ${\sim} 100$ square degree of data from the 
    HSC wide layer. 
    In this paper, we use this sample to 
    (a) measure individual \mden{} profiles for galaxies out to 100 kpc reliably with 
    the HSC data, 
    (b) examine the implications for the stellar mass function when the outer parts 
    of galaxies are accounted for, and
    (c) look at trends in outer envelope properties as a function of stellar mass. 
    In a second paper in this series, we will directly show the environmental dependence
    of the outer envelope mass (Huang\etal. in prep.)
    }

    \jenny{I suggest removing this here. I do not think it belongs in the Intro:
    Motivated by the ``two-phase'' scenario, and also due to the difficulty in 
    providing appropriate model to describe the \mstar{} distribution of massive 
    galaxy from its center to the very outskirt, we focus on \mstar{} within two 
    different physical apertures in this work:}
    \song{Since the original paper is quite long and complicated, we decide to define
    the two aperture masses in the beginning, and explain why they are important.
    For the new draft, I think it is Ok to do this later, but more comments on this 
    are welcomed!}

>>>>

    In this paper, we take advantage of new high-resolution (median 
    FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
    limit $> 28.5$\sb) imaging from the Hyper-Suprime Cam (HSC) Subaru Strategic 
    Program \citep[SSP,][]{HSCDR1} to characterize the outer parts of massive galaxies 
    as a function of their properties. 
    The deep imaging depth and excellent seeing conditions of HSC images make them 
    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
    large radii. 
    \update{
    With the help of reliable spectroscopic and photometric redshift 
    (e.g. the ones for \redm{} clusters, \citealt{Rykoff2014}; \citealt{Rozo2015b}),
    we select a large sample (${\sim} 7000$) of massive central galaxies at 
    $0.3 < z < 0.5$ using ${\sim} 100$ square degree of data from the 
    HSC wide layer. 
    In this paper, we use this sample to 
    (a) measure individual \mden{} profiles for galaxies out to 100 kpc reliably with 
    the HSC data, 
    (b) examine the implications for the stellar mass function (SMF) when the outer 
    parts of galaxies are accounted for, and
    (c) investigate the dependence of their outer envelopes on stellar mass.    
    In a second paper in this series, we will further look into the potential 
    environmental dependence of structures in massive ETGs (Huang\etal in prep.).
    }

    %\jenny{I suggest removing this here. I do not think it belongs in the Intro:
    %Motivated by the ``two-phase'' scenario, and also due to the difficulty in 
    %providing appropriate model to describe the \mstar{} distribution of massive 
    %galaxy from its center to the very outskirt, we focus on \mstar{} within two 
    %different physical apertures in this work:}
    %\song{Since the original paper is quite long and complicated, we decide to define
    %the two aperture masses in the beginning, and explain why they are important.
    %For the new draft, I think it is Ok to do this later, but more comments on this 
    %are welcomed!}
